Supplementary Information to "Improving Models to Predict Holocellulose and Klason Lignin Contents for Peat Soil Organic Matter with Mid Infrared Spectra

### 2022-03-03 analysis/paper/007-paper-m-prediction-differences.Rmd
Update manuscript 1, update formatting fo references.

```{r m-prediction-differences-1}
# create a data frame for plotting
d_pred_diff <-
  dplyr::bind_rows(
    dplyr::bind_rows(
    ## training data
    # Original Gaussian
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.2 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.2 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Gaussian"
      ) %>%
      dplyr::select(-spectra),
    # Original Beta
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.3 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.3 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Beta"
      ) %>%
      dplyr::select(-spectra),
    # Best all peaks
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.6 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.6 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best all peaks"
      ) %>%
      dplyr::select(-spectra),
    # Best binned spectra
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.10 %>%
          posterior_predict(newdata = d_underfitting[[4]]) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.7 %>%
          posterior_predict(newdata = d_underfitting[[1]]) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best binned spectra"
      ) %>%
      dplyr::select(-spectra)
    ) %>%
      dplyr::mutate(data_type = "Training"),

    dplyr::bind_rows(
    ## peat data
    # Original Gaussian
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.2 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.2 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Gaussian"
      ) %>%
      dplyr::select(-spectra),
    # Original Beta
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.3 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.3 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Beta"
      ) %>%
      dplyr::select(-spectra),
    # Best all peaks
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.6 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.6 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best all peaks"
      ) %>%
      dplyr::select(-spectra),
    # Best binned spectra
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.10 %>%
          posterior_predict(newdata = d_peat_bin50) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.7 %>%
          posterior_predict(newdata = d_peat_bin10) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best binned spectra"
      ) %>%
      dplyr::select(-spectra)
    ) %>%
      dplyr::mutate(data_type = "Peat") %>%
      dplyr::select(-dplyr::contains(c("holocellulose_hodgkins", "klason_lignin_hodgkins"))) %>%
      dplyr::bind_cols(purrr::map_df(1:4, function(x) d_peat_res)),

    dplyr::bind_rows(
    ## vegetation data
    # Original Gaussian
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.2 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.2 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Gaussian"
      ) %>%
      dplyr::select(-spectra),
    # Original Beta
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.3 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.3 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Beta"
      ) %>%
      dplyr::select(-spectra),
    # Best all peaks
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.6 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.6 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best all peaks"
      ) %>%
      dplyr::select(-spectra),
    # Best binned spectra
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.10 %>%
          posterior_predict(newdata = d_veg_bin50) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.7 %>%
          posterior_predict(newdata = d_veg_bin10) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best binned spectra"
      ) %>%
      dplyr::select(-spectra)
    ) %>%
      dplyr::mutate(data_type = "Vegetation") %>%
      dplyr::select(-dplyr::contains(c("holocellulose_hodgkins", "klason_lignin_hodgkins"))) %>%
      dplyr::bind_cols(purrr::map_df(1:4, function(x) d_veg_res))
  )

@@

d_pred_diff_intensities <-
  d_pred_diff_spectra %>%
  ir::ir_get_intensity(wavenumber = c(3400, 1200, 1550)) %>%
  ir::ir_drop_spectra() %>%
  tidyr::unnest(cols = "intensity") %>%
  tidyr::pivot_wider(names_from = x, values_from = y, names_prefix = "intensity_")
```

@@

p_pred_diff_train1_p1 <-
  d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1550) %>%
                  scale()
  ) %>%
  dplyr::filter(p_index) %>%
  ggplot(aes(x = hol_hat * 100, y = hol * 100)) +
  geom_point(aes(colour = scale(carb),
                 size = carb_rel)) +
  #geom_point(data = 
  #             d_pred_diff %>%
  #             dplyr::mutate(carb_rel = 
  #                
  #                  d_pred_diff_intensities %>%
  #                    dplyr::pull(intensity_1550)) %>%
  #             dplyr::filter(p_index & sample_id %in% d$sample_id[d$sample_type != "old magazines"][hol_sel]), 
  #           aes(x = hol_hat * 100, y = hol * 100,
  #               size = carb_rel), 
  #           fill = NA, shape = 21, colour = "grey50") +
  geom_abline(intercept = 0, slope = 1, colour = "grey50") +
  facet_wrap( ~ model) +
  guides(size = guide_legend(title = expression(Absorbance~at~1550~cm^{-1})),
         colour = guide_colourbar(title = "carb")) +
  labs(x = "Fitted values", y = "Measured values",
       title = "Holocellulose") +
  coord_fixed() +
  theme(legend.position = "bottom")

@@

d[d$sample_type != "old magazines", ][hol_sel, ]  %>%
  irpeat:::irp_content_klh_hodgkins_prepare() %>%
  hodgkins_ggplot() %>%
  wrap_plots()

d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1550)) %>%
  dplyr::filter(model == "Best binned spectra") %>%
  ggplot(aes(x = carb, y = (hol_hat - hol_hat_or) * 100)) +
  geom_point() +
  facet_grid(data_type ~ cut_number(carb_rel, 5))

@@

p1 <-
  d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1550)) %>%
  dplyr::filter(p1_index) %>%
  ggplot(aes(x = hol_hat * 100, y = hol_hat_or * 100)) +
  geom_point(aes(colour = carb,
                 size = carb_rel,
                 shape = data_type)) +
  geom_abline(intercept = 0, slope = 1, colour = "grey50") +
  facet_wrap( ~ model) +
  guides(size = guide_legend(title = "carb/OH-peak")) +
  labs(x = "Fitted values", y = "Measured values") +
  coord_fixed()

@@

# in the plots above, one can see that the model makes different predictions for two OM classes: needles and leaves and grasses. How do these spectra differ? It seem that this is mainly th region around 1550
d %>% 
  dplyr::filter(sample_type %in% c("needles", "leaves and grasses")) %>%
  plot() + 
  geom_path(aes(x = x, y = y, colour = sample_type, group = measurement_id)) +
  geom_vline(xintercept = 1550)
```

@@

p1 <-
  d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1550) %>%
                  scale()
  ) %>%
  dplyr::filter(p_index) %>%
  ggplot(aes(x = hol_hat * 100, y = hol_hat_or * 100)) +
  geom_point(aes(colour = scale(carb),
                 size = carb_rel)) +
  geom_abline(intercept = 0, slope = 1, colour = "grey50") +
  facet_wrap( ~ model) +
  guides(size = guide_legend(title = expression(Absorbance~at~1550~cm^{-1})),
         colour = guide_colourbar(title = "carb")) +
  labs(x = "Fitted values", y = "Fitted values (original model)",
       title = "Holocellulose") +
  coord_fixed() +
  theme(legend.position = "bottom")

@@

p_pred_diff_hol_intensity2 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1200 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1200 cm"^{-1}), 
       title = expression("Intensity at 1200 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity3 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1550 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1550 cm"^{-1}), 
       title = expression("Intensity at 1550 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

@@

p_pred_diff_hol_intensity4 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1200 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 3400 cm"^{-1}), 
       title = expression("Intensity at 3400 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity5 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1200 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1200 cm"^{-1}), 
       title = expression("Intensity at 1200 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity6 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1550 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1550 cm"^{-1}), 
       title = expression("Intensity at 1550 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

@@

d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb, hol_residuals, model)
  ) %>%
  dplyr::filter(p_index_test) %>%
  ggplot(aes(x = intensity_1200 %>% scale(), y = hol_residuals, colour = model)) + 
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(model ~ cut(carb, breaks = c(-1.45, -0.883, 0.454, 1.16))) +
  labs(y = "Prediction difference", x = expression("Intensity at 1200 cm"^{-1}), 
       title = expression("Intensity at 1200 cm"^{-1})) +
  guides(colour = guide_legend(title = "Data type")) +
  theme(legend.position = "bottom")

d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb, hol_residuals, model)
  ) %>%
  dplyr::filter(p_index_test) %>%
  ggplot(aes(x = intensity_1550 %>% scale(), y = hol_residuals, colour = model)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(model ~ cut(carb, breaks = c(-1.45, -0.883, 0.454, 1.16))) +
  labs(y = "Prediction difference", x = expression("Intensity at 1550 cm"^{-1}), 
       title = expression("Intensity at 1550 cm"^{-1})) +
  guides(colour = guide_legend(title = "Data type")) +
  theme(legend.position = "bottom")

>>>>

```{r m-prediction-differences-1}
# create a data frame for plotting
d_pred_diff <-
  dplyr::bind_rows(
    dplyr::bind_rows(
    ## training data
    # Original Gaussian
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.2 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.2 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Gaussian"
      ) %>%
      dplyr::select(-spectra),
    # Original Beta
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.3 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.3 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Beta"
      ) %>%
      dplyr::select(-spectra),
    # Best all peaks
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.6 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.6 %>%
          posterior_predict(newdata = d) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best all peaks"
      ) %>%
      dplyr::select(-spectra),
    # Best binned spectra
    d %>%
      dplyr::mutate(
        hol_hat =
          m1.8 %>%
          posterior_predict(newdata = d_underfitting[[2]]) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.8 %>%
          posterior_predict(newdata = d_underfitting[[2]]) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best binned spectra"
      ) %>%
      dplyr::select(-spectra)
    ) %>%
      dplyr::mutate(data_type = "Training"),

    dplyr::bind_rows(
    ## peat data
    # Original Gaussian
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.2 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.2 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Gaussian"
      ) %>%
      dplyr::select(-spectra),
    # Original Beta
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.3 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.3 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Beta"
      ) %>%
      dplyr::select(-spectra),
    # Best all peaks
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.6 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.6 %>%
          posterior_predict(newdata = d_peat_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best all peaks"
      ) %>%
      dplyr::select(-spectra),
    # Best binned spectra
    d_peat %>%
      dplyr::mutate(
        hol_hat =
          m1.8 %>%
          posterior_predict(newdata = d_peat_bin20) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.8 %>%
          posterior_predict(newdata = d_peat_bin20) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best binned spectra"
      ) %>%
      dplyr::select(-spectra)
    ) %>%
      dplyr::mutate(data_type = "Peat") %>%
      dplyr::select(-dplyr::contains(c("holocellulose_hodgkins", "klason_lignin_hodgkins"))) %>%
      dplyr::bind_cols(purrr::map_df(1:4, function(x) d_peat_res)),

    dplyr::bind_rows(
    ## vegetation data
    # Original Gaussian
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.2 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.2 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Gaussian"
      ) %>%
      dplyr::select(-spectra),
    # Original Beta
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.3 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        kl_hat = 
          m2.3 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Original Beta"
      ) %>%
      dplyr::select(-spectra),
    # Best all peaks
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.6 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.6 %>%
          posterior_predict(newdata = d_veg_res) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best all peaks"
      ) %>%
      dplyr::select(-spectra),
    # Best binned spectra
    d_veg %>%
      dplyr::mutate(
        hol_hat =
          m1.8 %>%
          posterior_predict(newdata = d_veg_bin20) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
         kl_hat = 
          m2.8 %>%
          posterior_predict(newdata = d_veg_bin20) %>%
          as.data.frame() %>%
          purrr::map_dbl(median),
        model = "Best binned spectra"
      ) %>%
      dplyr::select(-spectra)
    ) %>%
      dplyr::mutate(data_type = "Vegetation") %>%
      dplyr::select(-dplyr::contains(c("holocellulose_hodgkins", "klason_lignin_hodgkins"))) %>%
      dplyr::bind_cols(purrr::map_df(1:4, function(x) d_veg_res))
  )

@@

d_pred_diff_intensities <-
  d_pred_diff_spectra %>%
  ir::ir_get_intensity(wavenumber = c(3400, 1250, 1590)) %>%
  ir::ir_drop_spectra() %>%
  tidyr::unnest(cols = "intensity") %>%
  tidyr::pivot_wider(names_from = x, values_from = y, names_prefix = "intensity_")
```

@@

p_pred_diff_train1_p1 <-
  d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1590) %>%
                  scale()
  ) %>%
  dplyr::filter(p_index) %>%
  ggplot(aes(x = hol_hat * 100, y = hol * 100)) +
  geom_point(aes(colour = scale(carb),
                 size = carb_rel)) +
  #geom_point(data = 
  #             d_pred_diff %>%
  #             dplyr::mutate(carb_rel = 
  #                
  #                  d_pred_diff_intensities %>%
  #                    dplyr::pull(intensity_1590)) %>%
  #             dplyr::filter(p_index & sample_id %in% d$sample_id[d$sample_type != "old magazines"][hol_sel]), 
  #           aes(x = hol_hat * 100, y = hol * 100,
  #               size = carb_rel), 
  #           fill = NA, shape = 21, colour = "grey50") +
  geom_abline(intercept = 0, slope = 1, colour = "grey50") +
  facet_wrap( ~ model) +
  guides(size = guide_legend(title = expression(Absorbance~at~1590~cm^{-1})),
         colour = guide_colourbar(title = "carb")) +
  labs(x = "Fitted values", y = "Measured values",
       title = "Holocellulose") +
  coord_fixed() +
  theme(legend.position = "bottom")

@@

d[d$sample_type != "old magazines", ][hol_sel, ]  %>%
  irpeat:::irp_content_klh_hodgkins_prepare() %>%
  hkl_hodgkins_ggplot() %>%
  wrap_plots()

d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1590)) %>%
  dplyr::filter(model == "Best binned spectra") %>%
  ggplot(aes(x = carb, y = (hol_hat - hol_hat_or) * 100)) +
  geom_point() +
  facet_grid(data_type ~ cut_number(carb_rel, 5))

@@

p1 <-
  d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1590)) %>%
  dplyr::filter(p1_index) %>%
  ggplot(aes(x = hol_hat * 100, y = hol_hat_or * 100)) +
  geom_point(aes(colour = carb,
                 size = carb_rel,
                 shape = data_type)) +
  geom_abline(intercept = 0, slope = 1, colour = "grey50") +
  facet_wrap( ~ model) +
  guides(size = guide_legend(title = "carb/OH-peak")) +
  labs(x = "Fitted values", y = "Measured values") +
  coord_fixed()

@@

# in the plots above, one can see that the model makes different predictions for two OM classes: needles and leaves and grasses. How do these spectra differ? It seem that this is mainly th region around 1590
d %>% 
  dplyr::filter(sample_type %in% c("needles", "leaves and grasses")) %>%
  plot() + 
  geom_path(aes(x = x, y = y, colour = sample_type, group = measurement_id)) +
  geom_vline(xintercept = 1590)
```

@@

p1 <-
  d_pred_diff %>%
  dplyr::mutate(carb_rel = 
                  d_pred_diff_intensities %>%
                  dplyr::pull(intensity_1590) %>%
                  scale()
  ) %>%
  dplyr::filter(p_index) %>%
  ggplot(aes(x = hol_hat * 100, y = hol_hat_or * 100)) +
  geom_point(aes(colour = scale(carb),
                 size = carb_rel)) +
  geom_abline(intercept = 0, slope = 1, colour = "grey50") +
  facet_wrap( ~ model) +
  guides(size = guide_legend(title = expression(Absorbance~at~1590~cm^{-1})),
         colour = guide_colourbar(title = "carb")) +
  labs(x = "Fitted values", y = "Fitted values (original model)",
       title = "Holocellulose") +
  coord_fixed() +
  theme(legend.position = "bottom")

@@

p_pred_diff_hol_intensity2 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1250 cm"^{-1}), 
       title = expression("Intensity at 1250 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity3 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1950 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1590 cm"^{-1}), 
       title = expression("Intensity at 1590 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

@@

p_pred_diff_hol_intensity4 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 3400 cm"^{-1}), 
       title = expression("Intensity at 3400 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity5 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1250 cm"^{-1}), 
       title = expression("Intensity at 1250 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity6 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1590 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1590 cm"^{-1}), 
       title = expression("Intensity at 1590 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

@@

d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb, hol_residuals, model)
  ) %>%
  dplyr::filter(p_index_test) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_residuals, colour = model)) + 
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(model ~ cut(carb, breaks = c(-1.45, -0.883, 0.454, 1.16))) +
  labs(y = "Prediction difference", x = expression("Intensity at 1250 cm"^{-1}), 
       title = expression("Intensity at 1250 cm"^{-1})) +
  guides(colour = guide_legend(title = "Data type")) +
  theme(legend.position = "bottom")

d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb, hol_residuals, model)
  ) %>%
  dplyr::filter(p_index_test) %>%
  ggplot(aes(x = intensity_1590 %>% scale(), y = hol_residuals, colour = model)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(model ~ cut(carb, breaks = c(-1.45, -0.883, 0.454, 1.16))) +
  labs(y = "Prediction difference", x = expression("Intensity at 1590 cm"^{-1}), 
       title = expression("Intensity at 1590 cm"^{-1})) +
  guides(colour = guide_legend(title = "Data type")) +
  theme(legend.position = "bottom")
